Growth model analysis

### 2017-12-01 manuscriptAnalysis/MS_Analysis.Rmd
started adding counts of untagged fish

ggplot(d, aes(year,countPAllSpp)) +
  geom_point() +
  geom_line() +
  labs( x = "Year", y = "Estimated count") +
  theme_publication() +
  facet_grid(seasonGG ~ riverOrderedGG)

>>>>

ggplot(d, aes(year,countPAllSpp)) +
  geom_point() +
  geom_line() +
  labs( x = "Year", y = "Estimated count") +
#  ylim(0,2500) +
  theme_publication() +
  facet_grid(seasonGG ~ riverOrderedGG, scales = "free")
